Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-16 paper.tex
Reviewing section 4, Methodology, introduction. Closes #29

There is not a standard methodology to solve the general problem of sales forecasting. This is why the steps we have followed in this paper are those usually applied in a Knowledge Discovery in Databases (KDD) process \cite{fayyad1996data}. These are described in the following sections.

As a summary, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques are applied, such as Feature Selection (FS) \cite{kittler1986feature} (see Section \ref{subsec:data_preproces}). These methods check the relevance of all the variables of the patterns, aiming to reduce even more this set of features, in order to obtain easier-to-interpret models, in a less amount of time (due to their lower complexity), and with a fair or, hopefully, better accuracy.
This task may also help to identify leading indicators to be considered by a human expert to make predictions.

% You have to present the problem and not the solution. It's not "what
% you did last summer", it is SCIENCE. Why did you think FS was
% needed? What procedure did you use for it?
% Antonio - done
In this stage, both numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting 
methods.  
% Antonio - Should we speak about 'forecasting' or 'regression', Sam? Coudl they be used with the same meaning?

After this process (in Section \ref{subsec:select_method}), a selection of the best forecasting techniques have been conducted, looking for those rule- or tree-based, together with numerical methods which could yield the best results.

>>>>

There is not a standard methodology to solve the general problem of sales forecasting. However, the steps we have followed in this paper are those usually applied in a Knowledge Discovery in Databases (KDD) process \cite{fayyad1996data}. %These are described in the following sections.

Therefore, after the data has been collected and initially preprocessed (as described in previous section), other preprocessing techniques are applied, such as Feature Selection (FS) \cite{kittler1986feature}, which is portrayed in Section \ref{subsec:data_preproces}. These methods check the relevance of all the variables of the patterns, aiming to reduce even more this set of features, in order to obtain intelligible models, in a lesser amount of time due to their lower complexity, and usually without accuracy loss.
This task may also help to identify leading indicators to be considered by a human expert to make predictions.
% You have to present the problem and not the solution. It's not "what
% you did last summer", it is SCIENCE. Why did you think FS was
% needed? What procedure did you use for it?
% Antonio - done
In this stage, both numerical and visualisation-based approaches have been applied, in order to select the best variables for the forecasting 
methods.  
% Antonio - Should we speak about 'forecasting' or 'regression', Sam? Coudl they be used with the same meaning?

Next, Section \ref{subsec:select_method} reports a selection of the best forecasting techniques that have been conducted, looking for those rule- or tree-based, together with numerical methods which could yield the best results.
